Reformulating phylogenetic mixed models to improve flexibility and speed

### 2019-04-10 phyloglmm_ms.tex
minor edits

The simulations presented in this paper are an oversimplification of the real evolutionary processes in nature, but they are no simpler than what researchers typically use.
In fact, our simulations showed that even simple single predictor--response multi-species model can incorporate multiple levels of complexity (e.g. including random slopes, intercept-slope correlations, and the phylogenetic analog).
We have fitted models using different platforms that best match the simulation models. 
Models that cannot match the simulation (full) model are expected to perform poorly; it is important to understand the limitations and performance of these simpler models that are restricted by the commonly used methods available.
Using models that include some form of phylogenetic variation and residual variation is necessary to detect evolutionary process.
Here are a few points researchers should think about when fitting phylogenetic regression models.

>>>>

The simulations presented in this paper are an oversimplification of the real evolutionary processes in nature, but they are no simpler than what researchers typically use.
In fact, our results showed that even simple single predictor--response multi-species model can incorporate multiple levels of complexity (e.g. including random slopes, intercept-slope correlations, and the phylogenetic analog) and fitting

We have fitted models using different platforms that best match the simulation models. 
Models that cannot match the simulation (full) model are expected to perform poorly; it is important to understand the limitations and performance of these simpler models that are restricted by the commonly used methods available.
Using models that include some form of phylogenetic variation and residual variation is necessary to detect evolutionary process.
Here are a few points researchers should think about when fitting phylogenetic regression models.
